---
title: Zurich by the Numbers - Predictive Insights into Tourism Dynamic
author:
 - Name I, First Name I
 - Name II, First Name II
institute : University of Lausanne
date: today
title-block-banner: "#0095C8" #chosen for the university of lausanne
format:
  html:
    toc: true
    toc_float: true
    code-fold: true
    number-sections: true
    html-math-method: katex
    self-contained: true
    code-summary: "Click to show code"
    # pdf: default # use this if you want to render pdfs instead
abstract: |
  The following Forecasting project focuses on applying forecasting techniques to predict tourism trends in Zurich. This analysis aims to harness the power of historical data combined with forecasting algorithms to provide actionable insights into future tourism patterns. We engage in comprehensive data preparation, explore various predictive models, and conduct a detailed evaluation of their forecasting accuracy. The project encapsulates the challenge of turning complex data into understandable and strategic information, crucial for effective decision-making in Zurich's tourism sector.
---


```{r loading libraries, echo = FALSE, message = FALSE, warning = FALSE, include=FALSE}
# loading all the necessary packages
library(here)
source(here("docs/setup.R"))
library(fpp3)
library(fable)
library(tsibble)
library(dplyr)
library(lubridate)
library(plotly)
```

# DATA
## Cleaning
### Tourism Data - All
```{r Tourism ALL}
# Load the data in folder data named Dataset_tourism.xlsx)
tourism_data <- readxl::read_xlsx(here("data/Dataset_tourism.xlsx"))

#removing value 'Herkunftsland - Total' in column 'Herkunftsland' as it is just the total
tourism_data <- tourism_data %>% filter(Herkunftsland != "Herkunftsland - Total")
#print unique values in month column
unique(tourism_data$Monat)
# change ' [1] "Januar"    "Februar"   "März"      "April"     "Mai"       "Juni"      "Juli"      "August" "September" "Oktober"   "November"  "Dezember" into english month'
tourism_data$Monat <- tourism_data$Monat %>% recode_factor(
  "Januar" = "January",
  "Februar" = "February",
  "März" = "March",
  "April" = "April",
  "Mai" = "May",
  "Juni" = "June",
  "Juli" = "July",
  "August" = "August",
  "September" = "September",
  "Oktober" = "October",
  "November" = "November",
  "Dezember" = "December"
)
#add date type column for plotting purposes
tourism_data <- tourism_data %>% mutate(Date = dmy(paste("01", Monat, Jahr)))
#check for NAN
sum(is.na(tourism_data))
#analyse the NAN values, where are they
(tourism_data %>% filter(is.na(value)))
#show data using reactable only showing the first 100 rows
reactable::reactable(head(tourism_data, 1000))
```

### Tourism Data - Zurich
```{r Tourism Zurich}
#filter column 'Kanton' for Zurich
tourism_data_zurich <- tourism_data %>% filter(Kanton == "Zürich")
#check for NAN
sum(is.na(tourism_data_zurich))
#analyse the NAN values, where are they
tourism_data_zurich %>% filter(is.na(value))

#show the data in a table using reactable
reactable::reactable(head(tourism_data_zurich, 1000))
```

### Tourism Data - Zurich and Philipines

```{r Tourism Zurich and Philipines}
tourism_data_zurich_philippines <- tourism_data_zurich %>% filter(Herkunftsland == "Philippinen")
#show table using reactable
reactable::reactable(tourism_data_zurich_philippines)
```

### Deal with NAN

We have none in the data filtered with zurich and philippines, but if we would have we would :

#### Impute missing values ARIMA

If the missing values are random or if excluding them would result in a loss of valuable information, we might consider imputing them. One common approach is to use statistical models like ARIMA to interpolate missing values based on the patterns observed in the available data.

```{r}
# #Creating a tsibble with missing values
# data <- tourism_data_zurich_philippines %>%
#   as_tsibble(key = c(Kanton, Herkunftsland, Monat, Jahr)) %>%
#   select(Date, value) %>%
#   fill_gaps()
# 
# # Fit an ARIMA model to data with missing values
# model_fit <- data %>%
#   model(ARIMA(value))
# 
# # Interpolate missing values using the fitted ARIMA model
# filled_data <- model_fit %>%
#   interpolate(data)
# 
# # Print the data with filled in missing values
# print(filled_data)
```

# EDA - Zurich
## Zurich and All visiting countries

```{r}
# Preparing the data
#removing value 'Schweiz' in column 'Herkunftsland' as it is just the whole of Switzerland
tourism_data_zurich <- tourism_data_zurich %>% filter(Herkunftsland != "Schweiz")
data <- tourism_data_zurich %>%
  filter(!is.na(value)) %>%  # Removing rows with NA values in the 'value' column
  mutate(Monat = month(Date, label = TRUE, abbr = TRUE),  # Extract month from Date
         Jahr = year(Date)) %>%  # Extract year from Date
  group_by(Herkunftsland, Date) %>%  # Group by country and date
  summarise(Trips = sum(value), .groups = 'drop')  # Summing up trips for each country per date

p <- ggplot(data, aes(x = Date, y = Trips, group = Herkunftsland,
                      color = Herkunftsland == "Philippinen",
                      text = paste("Country:", Herkunftsland, "<br>Trips:", Trips))) +  # Added text for tooltip
  geom_line(show.legend = FALSE) +
  scale_color_manual(values = c("TRUE" = "red", "FALSE" = "grey")) +
  labs(title = "Number of Trips from Each Country to Zurich",
       x = "Date",
       y = "Number of Trips") +
  theme_minimal()

# Convert to an interactive plotly object
interactive_plot <- ggplotly(p, tooltip = "text")

# Adjust plotly settings 
interactive_plot <- interactive_plot %>%
  layout(margin = list(l = 60, r = 60, b = 60, t = 80),  # Adjust margins
         legend = list(orientation = "h", x = 0, xanchor = "left", y = -0.2))  # Adjust legend position

# Display the interactive plot
interactive_plot
```

## Zurich and Philipines Visitors
```{r}
# use tourism_data_zurich_philippines data to plot the values in y axis and Date in x axis
p <- ggplot(tourism_data_zurich_philippines, aes(x = Date, y = value)) +
  geom_line() +
  labs(title = "Number of Trips from Philipines to Zurich",
       x = "Date",
       y = "Number of Trips") +
  theme_minimal()
p
```

### Pattern
#### Decompose
```{r}
# Convert data to a time series object
tourism_ts <- tourism_data_zurich_philippines %>%
  arrange(Date) %>%
  # Ensure data is complete and monthly
  complete(Date = seq.Date(min(Date), max(Date), by = "month")) %>%
  replace_na(list(value = 0)) %>%  # Replace NA values if there are any
  # Create a time series object
  with(ts(value, frequency = 12, start = decimal_date(min(Date))))

# Decompose the time series
decomposed <- decompose(tourism_ts)

# Plot the decomposed components
plot(decomposed)
```

#### Seasonality

```{r}
# One chart

```

```{r}
# several chart per month

```